---
title: "PostProcessing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(tidybayes)
library(rstan)
library(devtools)
library(StanHeaders)
library(readxl)
library(data.table)
library(tidyr)
library(boot)
library(modelr)
library(tidyverse)
library(boot)
library(brms)
library(modelr)
library(tidybayes)
library(scales)
library(magrittr)
library(ggforce)

```

## R Markdown


The data itself, and some necessary mutations:

```{r data import and mutate}

exp_data <- read.csv("~/experiments/R_ResultsfromFirebase/results/20190420 pilot_2 data_trials.csv")
exp_participants <- read.csv("~/experiments/R_ResultsfromFirebase/results/20190420 pilot_2 data_participants.csv")
View(exp_data)
exp_data <- exp_data %>%
  filter(expType == "main")

exp_data <- exp_data %>%
  select(-data6, -data7,-data8,-data9,-data10,-questionListIndex, -additional_comment,-experimentName.y, -experimentName.x) %>%
  mutate(sessionMinutes = (sessionEndTime-sessionStartTime)/1000/60,
         trialSeconds = (trialEndTime - trialStartTime)/1000,
         selectedPercentage = selectedPercentage / 100,
         workerId = as.numeric(workerId))

restrict = function(x) ifelse(x == 0, 0.001, ifelse(x == 1, .999, x))

exp_data %<>%
  mutate(restricted_estimate = restrict(selectedPercentage))

exp_data <- exp_data %>%
  mutate(logit_estimated = logit(restricted_estimate),
         logit_real = logit(realPercentage))

```

Some very simple plots
```{r simple plots}
exp_data %>%
  ggplot(aes(x = selec, y = logit_estimated)) +
  geom_point(data = exp_data) 


```


Working models into it (this works, more or less, but is broadly uninteresting


```{r brms output}
simpleMLM = brm(logit_estimated ~ logit_real + (logit_real | workerId), exp_data, family = student())

pdf("~/MSThesis/simpleAbsError.pdf")
for(i in 1:10){

print(exp_data %>%
  data_grid(logit_real = seq_range(logit_real, n = 101), workerId) %>%
  add_predicted_draws(simpleMLM) %>%
  ggplot(aes(x = logit_real, y = abs(logit_real-logit_estimated))) +
  stat_lineribbon(aes(y = .prediction), .width = c(.95, .8, .5), color = "#08519C") +
  geom_point(data = exp_data, size = 2) +
  scale_fill_brewer() +
  facet_wrap_paginate(workerId, ncol = 3, nrow = 3, page = i))
}

dev.off()
```


A more complex model -- also works
```{r brms output}
complexMLM = brm(logit_estimated ~ logit_real + (logit_real | workerId|vis), exp_data, family = student())

pdf("~/MSThesis/complexAbsError.pdf")
for(i in 1:15){

print(exp_data %>%
  data_grid(logit_real = seq_range(logit_real, n = 101), workerId) %>%
  add_predicted_draws(simpleMLM) %>%
  ggplot(aes(x = logit_real, y = abs(logit_real-logit_estimated))) +
  stat_lineribbon(aes(y = .prediction), .width = c(.95, .8, .5), color = "#08519C") +
  geom_point(data = exp_data, size = 2) +
  scale_fill_brewer() +
  facet_wrap_paginate(.~workerId, ncol = 3, nrow = 2, page = i))
}
dev.off()
```

This doesn't work at all and probably never should.


```{r nonlinear brms, eval = FALSE}
priors_nonlin <- prior(normal(1,2), nlpar = "pow2") + prior(normal(0.5, 0.1), nlpar = "pow1") + prior(normal(0.05, 0.05),nlpar="pow0")
fit_nonlin <- brm(bf(error_absolute ~ (pow0 + pow1 * realPercentage + pow2 * realPercentage^2),  pow0 ~ 1|workerId, pow1 ~ 1|workerId, pow2 ~ 1|workerId, nl = TRUE), data = exp_data, prior = priors_nonlin)

saver = exp_data %>%
  data_grid(error_absolute = seq_range(realPercentage, n = 101), workerId) %>%
  add_predicted_draws(fit_nonlin) %>%
  ggplot(aes(x = realPercentage, y = error_absolute)) +
  stat_lineribbon(aes(y = .prediction), .width = c(.95, .8, .5), color = "#08519C") +
  geom_point(data = exp_data, size = 2) +
  scale_fill_brewer() +
  facet_wrap(~workerId)
```


In order to derive priors for Stan, we use the error results from Heer and Bostock's replication from Cleveland-McGill for the
mean and assume a normal distribution.

```{r Heer-Bostock priors}
out_label = c("Bar", "Pie", "Bubble")
out_mean = c(.014, .022, .027)
output = rbind(out_label,out_mean)
unscaled_absolute_error = out_mean^2
```